### 2017-10-21 src/2_Finance.tex
minor changes

A financial market is any marketplace where buyers and sellers participate
trading different assets such as equities, bonds, currencies and derivatives
(future or options). One of the main objectives of financial markets is to set
prices for global trade.
A financial market has many components but the most commonly used are money
markets and capital markets. Money markets are used for short-term basis,
usually for assets up to one year, for greater periods capital markets are used.
Capital markets include the stock or equity market and the bond or debt market
and their movements are the most widely followed \cite{aldridge2009}.

@@

This centralised structure existed until computer technology allowed a better
communication structure. Today financial markets are more decentralised
providing more liquidity. Exchanges and inter-dealer brokers were replaced by
liquidity pools or Electronic Communication Networks (ECNs) which are able to
transmit order quickly matching buyers and sellers optimally. There are also
dark liquidity pools where trader identity and orders remain anonymous.

>>>>

A financial market is any marketplace where buyers and sellers participate
trading different assets such as equities, bonds, currencies and derivatives
(future or options). One of the main objectives of financial markets is to set
prices for global trade.
A financial market has many components but the most commonly used are money
markets and capital markets. Money markets are used for short-term basis,
usually for assets up to one year, for greater periods, capital markets are used.
Capital markets include the stock or equity market and the bond or debt market
and their movements are the most widely followed \cite{aldridge2009}.

@@

This centralised structure existed until computer technology allowed a better
communication structure. Today financial markets are more decentralised
providing more liquidity. Exchanges and inter-dealer brokers were replaced by
liquidity pools or Electronic Communication Networks (ECNs) which are able to
transmit and order quickly matching buyers and sellers optimally. There are also
dark liquidity pools where trader identity and orders remain anonymous.
